### 2013-08-22 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
fixing the spn verification section. i am finally happy with this

In order to verify the correctness of the MCSA method and
implementation used for this work, MCSA solutions to the fuel assembly
problem with 1, 2, and 4 energy groups using $SP_1$ discretization
will be directly compared point-wise over all group and cell fluxes
computed by converging the criticality problem using both BiCGStab and
GMRES production implementations from the Trilinos scientific
computing library Aztec \cite{heroux_overview_2005}. In addition to
comparing the cell and group fluxes, the number of eigenvalue
iterations required to converge the problem along with the eigenvalue
itself will be compared as a means of verification. For the flux
values, we look to the 2-norm of the absolute difference between the
reference case and the comparison case in each energy group:
\begin{equation}
  || \ve{\Phi}_{ref}^g - \ve{\Phi}^g ||_2 < \epsilon_k\:,
  \label{eq:norm_comparison}
\end{equation}
such that this norm is less than the eigensolver tolerance,
$\epsilon_k$. For this work, the BiCGStab results will be taken as the
reference case. If the MCSA flux results satisfy
Eq~(\ref{eq:norm_comparison}), they will be deemed correct for the
purposes of this work. For the eigenvalues, we will look for the same
agreement within the tolerance of the eigensolver.

@@

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
$\epsilon_k = \sn{1}{-6}$ and a linear solver tolerance of \sn{1}{-8}
in a serial calculation. Table~\ref{tab:serial_ev_results} gives the
eigenvalue computed by each solver for each problem as well as the
number of eigenvalue iterations required to converge. For every
problem, each solver converged to the same eigenvalue up to the number
of digits reported by the eigensolver eigensolver in the same number
of eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.105987 \\
      GMRES-ILUT & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.105987 \\
      Richardson-ILUT & 1 & 25 & 1.105987 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.155239 \\
      GMRES-ILUT & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.155239 \\
      Richardson-ILUT & 2 & 35 & 1.155239 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.175850 \\
      GMRES-ILUT & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.175850 \\
      Richardson-ILUT & 4 & 31 & 1.175850 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}

Table~\ref{tab:serial_differences_g1},
Table~\ref{tab:serial_differences_g2}, and
Table~\ref{tab:serial_differences_g4} give the 2-norms of the cell
scalar fluxes difference vectors for all calculations and all energy
groups. All comparisons were performed within a group such that the
differences for the MCSA-ILUT-R-C results in group 3 for the 4-group
calculation were computed with the BiCGStab-ILUT solution in group 3
for the 4-group calculation as a reference. For all group flux results
given in the table, the maximum differences for all cases was less
than the linear solver tolerance used to converge the flux at each
eigenvalue iteration meaning that all values over the entire energy
and spatial domain are within these limits. Based on the flux results
and the eigenvalue results presented here, the MCSA results should be
deemed correct for the fuel assembly problem for serial calculations
with multiple energy groups.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \ve{\Phi}_{ref}^g - \ve{\Phi}^g ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{4.562}{-6} \\
      MCSA-ILUT-R-C & 0 & \sn{2.099}{-5} \\
      MCSA-ILUT-MR-C & 0 & \sn{4.812}{-5} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.371}{-5} \\
      MCSA-ILUT-MR-EV & 0 & \sn{3.605}{-5} \\
      Richardson-ILUT & 0 & \sn{1.531}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{BiCGStab is used as the
      reference. Each calculation was converged with the same
      eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \ve{\Phi}_{ref}^g - \ve{\Phi}^g ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{7.590}{-6} \\
      MCSA-ILUT-R-C & 0 & \sn{5.308}{-6} \\
      MCSA-ILUT-MR-C & 0 & \sn{6.387}{-5} \\
      MCSA-ILUT-R-EV & 0 & \sn{4.197}{-5} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.736}{-5} \\
      Richardson-ILUT & 0 & \sn{3.976}{-6} \\
      \hline
      GMRES-ILUT & 1 & \sn{7.579}{-6} \\
      MCSA-ILUT-R-C & 1 & \sn{1.645}{-5} \\
      MCSA-ILUT-MR-C & 1 & \sn{2.634}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{1.797}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{1.556}{-4} \\
      Richardson-ILUT & 1 & \sn{4.031}{-6} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{BiCGStab is used as the
      reference. Each calculation was converged with the same
      eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \ve{\Phi}_{ref}^g - \ve{\Phi}^g ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{2.376}{-5} \\
      MCSA-ILUT-R-C & 0 & \sn{2.639}{-5} \\
      MCSA-ILUT-MR-C & 0 & \sn{3.958}{-5} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.749}{-5} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.969}{-5} \\
      Richardson-ILUT & 0 & \sn{2.189}{-5} \\
      \hline
      GMRES-ILUT & 1 & \sn{2.271}{-5} \\
      MCSA-ILUT-R-C & 1 & \sn{3.702}{-5} \\
      MCSA-ILUT-MR-C & 1 & \sn{3.803}{-5} \\
      MCSA-ILUT-R-EV & 1 & \sn{4.142}{-5} \\
      MCSA-ILUT-MR-EV & 1 & \sn{2.723}{-5} \\
      Richardson-ILUT & 1 & \sn{2.137}{-5} \\
      \hline
      GMRES-ILUT & 2 & \sn{2.310}{-5} \\
      MCSA-ILUT-R-C & 2 & \sn{2.490}{-5} \\
      MCSA-ILUT-MR-C & 2 & \sn{2.214}{-5} \\
      MCSA-ILUT-R-EV & 2 & \sn{4.456}{-5} \\
      MCSA-ILUT-MR-EV & 2 & \sn{3.366}{-5} \\
      Richardson-ILUT & 2 & \sn{2.143}{-5} \\
      \hline
      GMRES-ILUT & 3 & \sn{2.335}{-5} \\
      MCSA-ILUT-R-C & 3 & \sn{3.045}{-5} \\
      MCSA-ILUT-MR-C & 3 & \sn{2.696}{-5} \\
      MCSA-ILUT-R-EV & 3 & \sn{1.946}{-4} \\
      MCSA-ILUT-MR-EV & 3 & \sn{3.295}{-5} \\
      Richardson-ILUT & 3 & \sn{2.161}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{BiCGStab is used as the
      reference. Each calculation was converged with the same
      eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g4}
\end{table}

>>>>

In order to verify the correctness of the MCSA method and
implementation used for this work, MCSA solutions to the fuel assembly
problem with 1, 2, and 4 energy groups using $SP_1$ discretization
will be directly compared point-wise over all group and cell fluxes
computed by converging the criticality problem using both BiCGStab and
GMRES production implementations from the Trilinos scientific
computing library Aztec \cite{heroux_overview_2005}. In addition to
comparing the cell and group fluxes, the number of eigenvalue
iterations required to converge the problem along with the eigenvalue
itself will be compared as a means of verification. For the flux
values, we look to the 2-norm and infinity norm of the relative
difference vector between the reference case and the comparison case
in each energy group:
\begin{equation}
  \text{Relative Difference} = \frac{\ve{\Phi}_{ref}^g -
    \ve{\Phi}^g}{\ve{\Phi}_{ref}^g}\:,
  \label{eq:relative_difference_vector}
\end{equation}
where the addition and subtraction operations are performed
element-wise to construct the vector. For this work, the BiCGStab
results will be taken as the reference case.

@@

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
\sn{1}{-6} and a linear solver tolerance of \sn{1}{-8} in a serial
calculation. Table~\ref{tab:serial_ev_results} gives the eigenvalue
computed by each solver for each problem as well as the number of
eigenvalue iterations required to converge. For every problem, each
solver converged to the same eigenvalue up to the number of digits
reported by the eigensolver eigensolver in the same number of
eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.105987 \\
      GMRES-ILUT & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.105987 \\
      Richardson-ILUT & 1 & 25 & 1.105987 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.155239 \\
      GMRES-ILUT & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.155239 \\
      Richardson-ILUT & 2 & 35 & 1.155239 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.175850 \\
      GMRES-ILUT & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.175850 \\
      Richardson-ILUT & 4 & 31 & 1.175850 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}

Table~\ref{tab:serial_differences_g1},
Table~\ref{tab:serial_differences_g2}, and
Table~\ref{tab:serial_differences_g4} give the infinity norms and
2-norms of the flux relative difference vectors given by
Eq~(\ref{eq:relative_difference_vector}) for all calculations and all
energy groups. In general, we see good agreement in the two norm
between the MCSA variants and the GMRES calculation, meaning that the
have approximately the same variation from the BiCGStab
calculation. We do note larger infinity norm values of this vector for
some of the MCSA variants (i.e. group 1 in the 2-group calculation),
however this large maximum value was not a global phenomenon with good
agreement in the 2-norm for the calculations. Based on the good
agreement between MCSA and GMRES for the relative difference of the
flux and the eigenvalue results presented here, the MCSA results
should be deemed correct for the fuel assembly problem for serial
calculations with multiple energy groups.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{4.562}{-6} & \sn{6.746}{-5} \\
      MCSA-ILUT-R-C & 0 & \sn{2.099}{-5} & \sn{2.541}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{4.812}{-5} & \sn{4.672}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.371}{-5} & \sn{2.740}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{3.605}{-5} & \sn{2.554}{-4} \\
      Richardson-ILUT & 0 & \sn{1.531}{-5} & \sn{2.771}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab is used as the reference. Each calculation was
      converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{7.590}{-6} & \sn{1.234}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{5.308}{-6} & \sn{1.066}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{6.388}{-5} & \sn{2.233}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{4.197}{-5} & \sn{2.168}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.736}{-5} & \sn{8.160}{-5} \\
      Richardson-ILUT & 0 & \sn{3.976}{-6} & \sn{7.059}{-5} \\
      \hline
      GMRES-ILUT & 1 & \sn{7.579}{-6} & \sn{1.246}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{1.645}{-5} & \sn{1.210}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{6.635}{-4} & \sn{9.435}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{1.797}{-4} & \sn{2.983}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{1.556}{-4} & \sn{2.055}{-4} \\
      Richardson-ILUT & 1 & \sn{4.031}{-6} & \sn{7.110}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab is used as the reference. Each calculation was
      converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{2.376}{-5} & \sn{4.043}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{2.639}{-5} & \sn{3.950}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{3.958}{-5} & \sn{4.635}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.749}{-5} & \sn{3.975}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.969}{-5} & \sn{4.054}{-4} \\
      Richardson-ILUT & 0 & \sn{2.189}{-5} & \sn{3.791}{-4} \\
      \hline
      GMRES-ILUT & 1 & \sn{2.271}{-5} & \sn{3.952}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{3.701}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{3.803}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{4.142}{-5} & \sn{4.011}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{2.723}{-5} & \sn{4.030}{-4} \\
      Richardson-ILUT & 1 & \sn{2.137}{-5} & \sn{3.768}{-4} \\
      \hline
      GMRES-ILUT & 2 & \sn{2.310}{-5} & \sn{4.021}{-4} \\
      MCSA-ILUT-R-C & 2 & \sn{2.490}{-5} & \sn{3.956}{-4} \\
      MCSA-ILUT-MR-C & 2 & \sn{2.214}{-5} & \sn{3.608}{-4} \\
      MCSA-ILUT-R-EV & 2 & \sn{4.456}{-5} & \sn{3.833}{-4} \\
      MCSA-ILUT-MR-EV & 2 & \sn{3.366}{-5} & \sn{3.797}{-4} \\
      Richardson-ILUT & 2 & \sn{2.143}{-5} & \sn{3.767}{-4} \\
      \hline
      GMRES-ILUT & 3 & \sn{2.335}{-5} & \sn{4.029}{-4} \\
      MCSA-ILUT-R-C & 3 & \sn{3.045}{-5} & \sn{3.963}{-4} \\
      MCSA-ILUT-MR-C & 3 & \sn{2.696}{-5} & \sn{3.606}{-4} \\
      MCSA-ILUT-R-EV & 3 & \sn{1.947}{-5} & \sn{4.283}{-4} \\
      MCSA-ILUT-MR-EV & 3 & \sn{3.295}{-5} & \sn{3.837}{-4} \\
      Richardson-ILUT & 3 & \sn{2.161}{-5} & \sn{3.772}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab is used as the reference. Each calculation was
      converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g4}
\end{table}
